---
title: "Creation of relevant Plots and Data for ANS Submission"
output: html_notebook
---



```{r}
## load up the packages we will need:  
require(igraph)
require(dplyr)
require(here)
require(ggcorrplot)

## ---------------------------

options(scipen = 6, digits = 4) # I prefer to view outputs in non-scientific notation
pallette <- c("#667c74", "#b3692b", "#c1ba7f", "#1f1918", "#bb8082")# this is needed on some PCs to increase memory allowance, but has no impact on mac

##------------------------Functions needed
readCSVs <- function(filename){
  object <- read.csv(paste0(here("data","dfs_final"),"/",filename))
  return(object)
}
#Test for normality
normalityTest <- function(df){
  df <- df
  object <- lapply(relevantCols,normalityTest_inside,df)
}

normalityTest_inside <- function(rel,df){
  return(shapiro.test(df[,rel]))
}
getPvalueInside <- function(df){
  if(df[[2]]<0.20){
    return("no normality")
  } else if(df[[2]]>0.20){
    return("normality given")
  }
 
}
getPvalue <- function(df){
  list <- lapply(df,getPvalueInside)
  return(list)
}
#Create Plots
createPlot <- function(index){
  corr <- round(cor(DFs[[index]] %>%
                      select(k_shell,num_clusters,degree,community_centrality,total_infection,communities_louvain)
  ,method = "spearman"), 2)
  p.mat <- cor_pmat(DFs[[index]] %>%
                      select(k_shell,num_clusters,degree,community_centrality,total_infection,communities_louvain))
  
  p <- ggcorrplot(corr, hc.order = TRUE, type = "lower",
             p.mat = p.mat,
             lab = TRUE,
             outline.col = "white",
             ggtheme = ggplot2::theme_gray,
             colors = c("#6D9EC1", "white", "#E46726"))+labs(title = DFs_files_list[[index]])
  
  return(p)
}

```

## Import Networks
First things first. Let's import the newly generated DFs with Community Size Info
```{r}
#Create list of DFs
DFs_files_list <- list.files(paste0(here("data","dfs_final"),"/"))

#Import DFs
DFs <- lapply(DFs_files_list,readCSVs)


```

## Check normality
Check relevant measures for assumption of normality
```{r}
relevantCols <- c(2,3,4,5,10,11)
relevantColNames <- c("k_shell","degree","community_centrality","num_clusters","communities_louvain","communities_LinkComm")

save <- lapply(DFs,normalityTest)
normalities <- lapply(save,getPvalue)
normalities <- lapply(normalities,as.data.frame)
normalities <- lapply(normalities,setNames,relevantColNames)

normalities
```
## Correlations

No normality can be assumed for any of the measures. Get Correlations of ENC_lv (Louvain) and ENC_lc (LinkComm) with other Measures

```{r}

measuresVector <- c("k_shell","degree","community_centrality","peak_infection","total_infection")

getCorrelations_ENC_lv <- function(df){
  output <- numeric()
  c(output,as.numeric(df %>%
    summarise(cor(communities_louvain,k_shell,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_louvain,degree,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_louvain,community_centrality,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_louvain,peak_infection,method = "spearman")))) -> output
   c(output,as.numeric(df %>%
    summarise(cor(communities_louvain,total_infection,method = "spearman")))) -> output
 return(as.numeric(output))
}

getCorrelations_ENC_lc <- function(df){
  output <- numeric()
  c(output,as.numeric(df %>%
    summarise(cor(communities_LinkComm,k_shell,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_LinkComm,degree,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_LinkComm,community_centrality,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_LinkComm,peak_infection,method = "spearman")))) -> output
  c(output,as.numeric(df %>%
    summarise(cor(communities_LinkComm,total_infection,method = "spearman")))) -> output
  return(as.numeric(output))
}


corr_df_lc <- as.data.frame(cbind(measuresVector,as.data.frame(sapply(DFs,getCorrelations_ENC_lc))))
corr_df_lv <- as.data.frame(cbind(measuresVector,as.data.frame(sapply(DFs,getCorrelations_ENC_lv))))

names(corr_df_lc) <- c("measure",DFs_files_list)
names(corr_df_lv) <- c("measure",DFs_files_list)

corr_df_lc
corr_df_lv
```
## Mean and SD Correlations
Get mean correlation and sd correlation for corr_df_lc (LinkComm) and corr_df_lv (Louvain)
```{r}
corr_df_lc %>%
  rowwise(measure)%>%
  summarise(mean_corr_df_lc = mean(c(network_1.csv,
                           network_2.csv,
                           network_3.csv,
                           network_4.csv,
                           network_5.csv,
                           network_6.csv,
                           network_7.csv,
                           network_8.csv)),
            sd_corr_df_lc=sd(c(network_1.csv,
                           network_2.csv,
                           network_3.csv,
                           network_4.csv,
                           network_5.csv,
                           network_6.csv,
                           network_7.csv,
                           network_8.csv)))

corr_df_lv %>%
  rowwise(measure)%>%
  summarise(mean_corr_df_lv = mean(c(network_1.csv,
                           network_2.csv,
                           network_3.csv,
                           network_4.csv,
                           network_5.csv,
                           network_6.csv,
                           network_7.csv,
                           network_8.csv)),
            sd_corr_df_lv=sd(c(network_1.csv,
                           network_2.csv,
                           network_3.csv,
                           network_4.csv,
                           network_5.csv,
                           network_6.csv,
                           network_7.csv,
                           network_8.csv)))
```
## Plots of Correlations

Now, we want to plot these values.
```{r}
library(reshape2)
library(wesanderson)

#prepare dfs for plot (remove one col)
corr_df_lc %>%
       select(-measure) -> corr_df_lc_plot
corr_df_lv %>%
       select(-measure) -> corr_df_lv_plot

#plot first with melt
cbind(melt(corr_df_lc_plot,measure.vars = colnames(corr_df_lc_plot)),measure = as.factor(measuresVector)) %>% ggplot(.,aes(x=variable,y=value,color=measure))+geom_line(aes(group=measure))+geom_point(aes(color=measure),size=3,shape = 21, 
               stroke = 2.0,fill="white")+scale_color_manual(values=pallette)+ylab("Spearman's Correlation")+xlab("network")+labs(title = "Correlations of ENC_lc with other Measures")

#plot second with melt
cbind(melt(corr_df_lv_plot,measure.vars = colnames(corr_df_lv_plot)),measure = as.factor(measuresVector)) %>% ggplot(.,aes(x=variable,y=value,color=measure))+geom_line(aes(group=measure))+geom_point(aes(color=measure),size=3,shape = 21, 
               stroke = 2.0,fill="white")+scale_color_manual(values=pallette)+ylab("Spearman's Correlation")+xlab("network")+labs(title = "Correlations of ENC_lv with other Measures")
```
#Avg. Peak Infection across Networks
```{r}
getAvgPeakInfection <- function(df){
  df%>%
  summarise(mean(peak_infection)) -> output
  return(as.numeric(output))
}


avgPeakInfections <- cbind(DFs_files_list,as.data.frame(sapply(DFs,getAvgPeakInfection)))
names(avgPeakInfections) <- c("network","avgPeakInfection")

avgPeakInfections
```
##Plot of avg. Peak Infections
```{r}
avgPeakInfections %>%
  ggplot(aes(x=network,y=avgPeakInfection))+geom_line(aes(group = 1),color="#b3692b")+geom_point(color="#b3692b",size=3,shape = 21,stroke = 2.0,fill="white")+ylab("Peak Infection")+xlab("network")+labs(title = "Avg Peak Infection across networks")
         
      
```

##Imprecision Function
```{r}
getImprecision_total <- function(df){
    top_spreader <- as.numeric(df%>%
                      arrange(desc(total_infection))%>%
                      slice_head(prop = 0.1)%>%
                      summarise(mean(total_infection)))
    output <- numeric()
    c(output,as.numeric(1-(df%>%
               arrange(desc(k_shell))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(total_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(degree))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(total_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(community_centrality))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(total_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(communities_louvain))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(total_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(communities_LinkComm))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(total_infection)))/top_spreader)) -> output
    return(output)
}

getImprecision_peak <- function(df){
    top_spreader <- as.numeric(df%>%
                      arrange(desc(peak_infection))%>%
                      slice_head(prop = 0.1)%>%
                      summarise(mean(peak_infection)))
    output <- numeric()
    c(output,as.numeric(1-(df%>%
               arrange(desc(k_shell))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(peak_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(degree))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(peak_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(community_centrality))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(peak_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(communities_louvain))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(peak_infection)))/top_spreader)) -> output
    c(output,as.numeric(1-(df%>%
               arrange(desc(communities_LinkComm))%>%
               slice_head(prop = 0.1)%>%
               summarise(top_measure = mean(peak_infection)))/top_spreader)) -> output
    return(output)
}

measures <- c("k_shell","degree","community_centrality","communities_louvain","communities_LinkComm")

imprecision_total <- cbind(measures,as.data.frame(sapply(DFs,getImprecision_total)))
imprecision_peak <- cbind(measures,as.data.frame(sapply(DFs,getImprecision_peak)))

names(imprecision_total) <- c("measure",DFs_files_list)
names(imprecision_peak) <- c("measure",DFs_files_list)

imprecision_peak
imprecision_total
```

##Imprecision Plots
Now plot it 
```{r}
imprecision_total %>%
       select(-measure) -> imprecision_total_plot
imprecision_peak %>%
       select(-measure) -> imprecision_peak_plot

#plot first with melt
cbind(melt(imprecision_total_plot,measure.vars = colnames(imprecision_total_plot)),measure = as.factor(measures)) %>% ggplot(.,aes(x=variable,y=value,color=measure))+geom_line(aes(group=measure))+geom_point(aes(color=measure),size=3,shape = 21, 
               stroke = 2.0,fill="white")+scale_color_manual(values=pallette)+ylab("Imprecision")+xlab("network")+labs(title = "Imprecision Function (total_infection)")

#plot second with melt
cbind(melt(imprecision_peak_plot,measure.vars = colnames(imprecision_peak_plot)),measure = as.factor(measures)) %>% ggplot(.,aes(x=variable,y=value,color=measure))+geom_line(aes(group=measure))+geom_point(aes(color=measure),size=3,shape = 21, 
               stroke = 2.0,fill="white")+scale_color_manual(values=pallette)+ylab("Imprecision")+xlab("network")+labs(title = "Imprecision Function (peak_infection)")
```

##Bivariate Plots
Now we want to take a look at the bivariate plots. Firstly, create the functions.

```{r}
library(viridis)

createBivariatePlot <- function(index,measure_x,measure_y,infection){
  
  DFs[[index]]%>%
  ggplot(aes_string(x=measure_x,y=measure_y))+
  geom_jitter(aes_string(color=infection))+scale_color_viridis(option = "inferno")+
  theme_minimal()+labs(title = DFs_files_list[index])->plot
  
  return(plot)
}
```

Now, create the plots

```{r}
plots_cc_ks_total <- lapply(1:8,createBivariatePlot,"community_centrality","k_shell","total_infection")
plots_cc_ks_peak <- lapply(1:8,createBivariatePlot,"community_centrality","k_shell","peak_infection")
plots_cc_d_total <- lapply(1:8,createBivariatePlot,"community_centrality","degree","total_infection")
plots_cc_d_peak <- lapply(1:8,createBivariatePlot,"community_centrality","degree","peak_infection")
plots_enclv_ks_total <- lapply(1:8,createBivariatePlot,"communities_louvain","k_shell","total_infection")
plots_enclv_ks_peak <- lapply(1:8,createBivariatePlot,"communities_louvain","k_shell","peak_infection")
plots_enclv_cc_total <- lapply(1:8,createBivariatePlot,"communities_louvain","community_centrality","total_infection")
plots_enclv_cc_peak <- lapply(1:8,createBivariatePlot,"communities_louvain","community_centrality","peak_infection")
plots_enclc_ks_total <- lapply(1:8,createBivariatePlot,"communities_LinkComm","k_shell","total_infection")
plots_enclc_ks_peak <- lapply(1:8,createBivariatePlot,"communities_LinkComm","k_shell","peak_infection")
plots_enclc_cc_total <- lapply(1:8,createBivariatePlot,"communities_LinkComm","community_centrality","total_infection")
plots_enclc_cc_peak <- lapply(1:8,createBivariatePlot,"communities_LinkComm","community_centrality","peak_infection")

plots_cc_ks_total
plots_cc_ks_peak
plots_cc_d_total
plots_cc_d_peak
plots_enclv_ks_total
plots_enclv_ks_peak
plots_enclv_cc_total
plots_enclv_cc_peak
plots_enclc_ks_total
plots_enclc_ks_peak
plots_enclc_cc_total
plots_enclc_cc_peak
```

#Gini Coefficients
```{r}
require(ineq)

getGini <- function(df){
  return(ineq(df$degree,type = "Gini"))
}

sapply(DFs, getGini)

```

